---
title: "Profile"
description: "My Assignment"
output: distill::distill_article
---
## My work

This page shows my academic and data analysis work.

### Distribution of mothers’ ages in the dataset

## Data visualisation project

This project explores the distribution of UK constituency sizes.

```{r}

ggplot(kidiq_2, aes(x = mom_age)) +
  geom_histogram(aes(y = after_stat(density)),
                 binwidth = 2,
                 fill = "#2C7FB8",
                 colour = "white",
                 alpha = 0.8) +
  geom_density(colour = "#08306B", linewidth = 1.2) +
  geom_vline(aes(xintercept = mean(mom_age, na.rm = TRUE)),
             colour = "red",
             linetype = "dashed",
             linewidth = 1) +
  labs(
    title = "Distribution of Mothers' Ages",
    subtitle = "Histogram with density curve and mean age",
    x = "Mother's Age",
    y = "Density",
    caption = "Source: kidiq dataset"
  ) +
  theme_minimal(base_size = 14)
  
```


### Data analysis project
This project uses the kidiq dataset to explore the distribution of mothers’ ages at the time of childbirth. The histogram shows how frequently different ages appear in the dataset. Most mothers in the sample are between 20 and 25 years old, with fewer observations at younger and older ages. This suggests that childbirth in the dataset is most common in the early twenties.


This analysis demonstrates how R and ggplot2 can be used to visualise distributions and identify patterns in data.

### Research essay
In my research essay, I analysed political behaviour using empirical evidence from course readings and datasets. The essay focused on how social and economic factors influence political outcomes. By combining theoretical arguments with data analysis, the research aimed to better understand patterns in political behaviour.

### Skills

- R programming for data analysis

- Data visualisation using ggplot2


- Interpreting statistical distributions

- Communicating insights using visual evidence

- Political analysis and research writing

---

#This visualisation shows the most frequent political terms in the sample text after removing common stop words. Terms such as democracy, voting, and representation appear most often, highlighting the central themes of political participation and democratic engagement.

```{r}
library(tidytext)
library(dplyr)
library(ggplot2)

text <- data.frame(
  line = 1:3,
  text = c(
    "Democracy depends on participation and representation.",
    "Voting turnout and political engagement are central to democratic politics.",
    "Representation, democracy and voting are key themes in political analysis."
  )
)

words <- text %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

word_counts <- words %>%
  count(word, sort = TRUE) %>%
  slice_max(n, n = 10)


ggplot(word_counts, aes(x = reorder(word, n), y = n)) +
  geom_col(fill = "#2C7FB8", width = 0.7) +
  coord_flip() +
  labs(
    title = "Most frequent political terms",
    subtitle = "Word frequency after removing common stop words",
    x = "",
    y = "Frequency"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(size = 11, colour = "grey40"),
    panel.grid.major.y = element_blank()
  )
```
  

The results show that words such as *democracy*, *voting*, and *representation* appear most frequently. This highlights the central themes of political participation and democratic engagement within the text.

## Skills

- R programming  
- Data visualisation  
- Text analysis  
- Political data analysis  
- Reproducible research

  
---
